\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-27 doc/flexiblesusy-paper.tex
add table with pole mass and time comparison
round times
describe pole mass calculation comparison table

\item \code{HighPrecision}: This option solves
  Eq.~\eqref{eq:pole-mass-def} exactly by iterating over the momentum
  $p$.  It therefore provides the determination of the pole masses
  with highest precision, but has also the highest execution time.
  Here the one-loop mass matrix $m_{f,1L}^\text{high}$ is diagonalized
  $n$ times, as in the case of \code{MediumPrecision},
  resulting in $n$ pole masses $m_{f_k}^\pole$ ($k = 1,\ldots,n$).
  Afterwards, the diagonalization is repeated, this time using the
  calculated pole masses $m_{f_k}^\pole$ for the momentum calculation
  $p^2 = (m_{f_k}^\pole)^2$.  The iteration stops if convergence is
  reached.
\end{itemize}
%
If higher accuracy is required, two-loop corrections to the
self-energies can be added by setting \code{UseHiggs2LoopMSSM = True}
in the MSSM or \code{UseHiggs2LoopNMSSM = True} in the NMSSM in the
model file.  The former provides routines that call the two-loop Higgs
FORTRAN routines supplied by P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
for calculating corrections of $\oatas$, $\oabas$, $\oatq$, $\oabq$,
$\oatauq$ and $\oatab$.  The latter adds corrections calculated in the
NMSSM at $\oatas$, $\oabas$ from \cite{Degrassi:2009yq} and partial
corrections for the order $\oatq$, $\oabq$, $\oatauq$ and $\oatab$ from the
MSSM.  These corrections can then be included in the
calculation of the Higgs pole masses when running the spectrum
generator by setting the appropriate SLHA flags.

>>>>

\item \code{HighPrecision}: This option solves
  Eq.~\eqref{eq:pole-mass-def} exactly by iterating over the momentum
  $p$.  It therefore provides the determination of the pole masses
  with highest precision, but has also the highest execution time.
  Here the one-loop mass matrix $m_{f,1L}^\text{high}$ is diagonalized
  $n$ times, as in the case of \code{MediumPrecision},
  resulting in $n$ pole masses $m_{f_k}^\pole$ ($k = 1,\ldots,n$).
  Afterwards, the diagonalization is repeated, this time using the
  calculated pole masses $m_{f_k}^\pole$ for the momentum calculation
  $p^2 = (m_{f_k}^\pole)^2$.  The iteration stops if convergence is
  reached.
\end{itemize}
%
A numerical comparison of the three different methods for a specific
CMSSM parameter point can be found in
\tabref{tab:pole-mass-precision-comparison}.  One finds that (i) the
calculated lightest CP-even Higgs pole mass is sensitive to the chosen
pole mass calculation method due to the large loop corrections.
Especially, if two-loop contributions to the Higgs tadpoles and
self-energies are added, the two approximations \code{LowPrecision}
and \code{MediumPrecision} must not be used, because they neglect
terms of two-loop order.  (ii) Since the gluino does not mix with
other particles, there is no difference between \code{LowPrecision}
and \code{MediumPrecision}.  Not neglecting the two-loop terms by
using \code{HighPrecision} changes the gluino mass about $1\unit{\%}$.
(iii) Since the up-type squarks form a $6$-plet, the calculation of
their pole masses is dramatically increased from $2.57\unit{ms}$ to
$60.9\unit{ms}$ between \code{LowPrecision} and \code{HighPrecision}.
However, since the change in the lightest up-type squark mass between
the three different methods is only of the order $\unit{0.4\%}$, one
can consider calculating then with \code{MediumPrecision} only.
%
\begin{table}[tbh]
  \centering
  \begin{tabular}{llll}
    \toprule
    & \code{LowPrecision}
    & \code{MediumPrecision}
    & \code{HighPrecision}\\
    \midrule
    $m_h$
    & $1441\unit{GeV}$ ($0.96\unit{ms}$)
    & $128\unit{GeV}$ ($2.53\unit{ms}$)
    & $126\unit{GeV}$ ($9.79\unit{ms}$) \\
    $m_{\tilde{g}}$
    & $10167\unit{GeV}$ ($0.10\unit{ms}$)
    & $10167\unit{GeV}$ ($0.10\unit{ms}$)
    & $10251\unit{GeV}$ ($0.41\unit{ms}$) \\
    $m_{\tilde{u}_1}$
    & $8702\unit{GeV}$ ($2.57\unit{ms}$)
    & $8714\unit{GeV}$ ($15.7\unit{ms}$)
    & $8734\unit{GeV}$ ($60.9\unit{ms}$) \\
    \bottomrule
  \end{tabular}
  \caption{Comparison of pole masses with different calculation
    methods for the CMSSM with $m_0=8\unit{TeV}$, $M_{1/2}=A_0=5\unit{TeV}$,
    $\tan\beta=20$, $\sign\mu=+1$.  In brackets the time used to calculate
    the pole masses of the whole multiplet is given.}
  \label{tab:pole-mass-precision-comparison}
\end{table}
%

If higher accuracy is required, two-loop corrections to the
self-energies can be added by setting \code{UseHiggs2LoopMSSM = True}
in the MSSM or \code{UseHiggs2LoopNMSSM = True} in the NMSSM in the
model file.  The former provides routines that call the two-loop Higgs
FORTRAN routines supplied by P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
for calculating corrections of $\oatas$, $\oabas$, $\oatq$, $\oabq$,
$\oatauq$ and $\oatab$.  The latter adds corrections calculated in the
NMSSM at $\oatas$, $\oabas$ from \cite{Degrassi:2009yq} and partial
corrections for the order $\oatq$, $\oabq$, $\oatauq$ and $\oatab$ from the
MSSM.  These corrections can then be included in the
calculation of the Higgs pole masses when running the spectrum
generator by setting the appropriate SLHA flags.
